Scalar and Representative Observables, and Their Associated Statistial Model, for Polarimetric SAR Data

### 2013-11-14 Remote_Sensing_Letter/paper.tex
ready for submission

\begin{abstract}
%Problem statement
This paper proposes scalar and representative observables,
  including several statistically consistent discrimination measure
  that are vitally important in the processing of multi-dimensional POLSAR data.
%This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
%  which includes several statistically consistent discrimination measures. %can be derived.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
  which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implications are that %of the proposed approach is that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

Statistical models are the foundation for discrimination measures in both SAR and POLSAR.
For the more matured SAR field, 
  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \citep{Rignot_1993_TGRS_896}.
For the less matured POLSAR field the same case should apply, 
  except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \citep{Conradsen_2003_TGRS_4}.

@@

The models in Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:change_ratio_distribution} are now validated against real-life captured data.
Each model requires the estimation of two parameters from the data; 
the dimensional number $d$, and  the look number $L$.
$d$ is related to the type of (POL)SAR data captured,
  with $d=1,2,3$ corresponding to the cases of SAR, partial and full POLSAR, respectively.
$L$ is normally stated by the data provider,
  but in this section it is estimated using the technique proposed by \citet{Anfinsen_2009_TGRS_3795}.

To show the robustness of the proposed models, 
  their validations are carried out on two different POLSAR sensors: (1) airborne four-look ($L=4$) AIRSAR Flevoland image and (2)
fine-quad single-look ($L=1$) complex RADARSAT2 image.
Since the determinant of the covariance matrix is only significant on multi-look data,
  nine-look processing is first applied to the single-look data ($L=9$).

>>>>

\begin{abstract}
%Problem statement
This paper proposes novel scalar and representative observables,
  including several statistically consistent discrimination measures,
  that are particularly useful in the interpretation and processing of multi-dimensional POLSAR data.
%This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
%  which includes several statistically consistent discrimination measures. %can be derived.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
  which is shown applicable to both two and three dimensional versions of partial and full monostatic POLSAR data.
As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implications of the proposed approach are that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

Statistical models are the foundation for discrimination measures in both SAR and POLSAR.
For the more matured SAR field, 
  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \citep{Rignot_1993_TGRS_896}.
For the less matured POLSAR field the same case should apply, 
  except that so far only asymptotic distributions have been derived for the most common foundation: likelihood test statistics \citep{Conradsen_2003_TGRS_4}.

@@

The models in Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:change_ratio_distribution} are now validated against real-life captured data.
Each model requires the estimation of two parameters from the data; 
the dimensional number $d$, and  the look number $L$.
$d$ is related to the type of (POL)SAR data captured,
  with $d=1,2,3$ corresponding to the cases of SAR, partial and full POLSAR, respectively.
$L$ is normally stated by the data provider,
  but in this section it is estimated using the technique proposed by \citet{Anfinsen_2009_TGRS_3795}.
To show the robustness of the proposed models, 
  their validations are carried out on two different POLSAR sensors: (1) airborne four-look ($L=4$) AIRSAR Flevoland image and (2)
fine-quad single-look ($L=1$) complex RADARSAT2 image.
Since the determinant of the covariance matrix is only significant on multi-look data,
  nine-look processing is first applied to the single-look data ($L=9$).
